Need for Suboptimal Time management in Non-ideal Shared space

### 2015-04-11 paper.tex
Minor updates in Introduction

The following contents of the paper are divided into four sections. Section II. Existing literature would focus on some of the existing techniques for Time management. Followed by Section III. Execution and Evaluation which is completely spanned by a case study where the subject employs an adaptive time management technique for their day to day activity for two fortnights. We will then conclude with Section IV. Conclusions, where would be highlighting the key aspects of our argument and how we derived or observed them in the case of the test subject.

>>>>

The following contents of the paper are divided into four sections. Section II - Existing literature, would focus on some of the existing techniques for Time management. Followed by Section III - Execution and Evaluation, which is completely spanned by a case study where the subject employs an adaptive time management technique for their day to day activity for two fortnights. We will then conclude with Section IV - Conclusions, where would be highlighting the key aspects of our argument and how we derived or observed them in the case of the test subject.
